---
title: "Custom Filters"
author: "Ernest Benedito"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Custom Filters}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

It is also possible to write your own filters used with `MessageHandler` and `CommandHandler`. In essence, a filter is simply a function that receives a `Message` instance and returns either `TRUE` or `FALSE`. If a filter evaluates to `TRUE`, the message will be handled. 

### Restricting users

For the `kill` example we saw in the [previous page](https://github.com/ebeneditos/telegram.bot/wiki/Basic-Functionalities#stopping-the-bot), it would be useful to filter that command so to make it accessible only for a specific `<user-id>`. Thereby, you could add a filter:

```{r, eval = F}
filter_user <- function(message){
                   message$from_user  == <user-id>
               }
```	       

Now, you could update the handler with this filter:

```{r, eval = F}
kill_handler <- CommandHandler('kill', kill, filter_user)
```

### Text or command filter

Filters can also be added to the `Filters` object. Within it, we can see that `Filters$text` and `Filters$command` are mutually exclusive, so we could add a filter for messages that can be either one of them. This would result as:

```{r, eval = F}
Filters$text_or_command <- function(message){
                               !is.null(message$text)
                           }
```
