---
title: "Tutorial – Building an R Bot in 3 steps"
author: "Ernest Benedito"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial – Building an R Bot in 3 steps}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this tutorial we will explain how to build a Bot with R and `telegram.bot` following the next steps:

1. Creating the `Updater` object
2. The first function
3. Starting the Bot

First, though, let's introduce the `telegram.bot` package.

### Introduction

In order to build a bot that is continuously running and is able to respond to multiple input data formats, the `telegram.bot` package features several `R6` classes, but the two most important ones here are `Updater` and `Dispatcher`.

The `Updater` class continuously fetches new updates from Telegram and passes them on to the `Dispatcher` class.  If you create an `Updater` object, it will create a `Dispatcher`. You can then register handlers of different types in the `Dispatcher`, which will sort the updates fetched by the `Updater` according to the handlers you registered, and deliver them to a callback function that you defined. Every handler is an instance of any subclass of the `Handler` class.

To begin, you'll need an Access Token. If you already read and followed [Introduction to the API](https://github.com/ebeneditos/telegram.bot/wiki/Introduction-to-the-API), you can use the one you generated then. If not: To generate an Access Token, you have to talk to [*@BotFather*](https://telegram.me/botfather) and follow a few simple steps (described [here](https://core.telegram.org/bots#6-botfather)). You should really read the introduction first, though.

With that said, let's *get started!*

### 1. Creating the Updater object

First, you first must create an `Updater` object. Replace `TOKEN` with your Telegram Bot's API Access Token, which looks something like `123456:ABC-DEF1234ghIkl-zyx57W2v1u123ew11`.

```{r, eval = FALSE}
library(telegram.bot)

updater <- Updater(token = "TOKEN")
```

**Recommendation:** Following [Hadley's API
guidelines](http://github.com/hadley/httr/blob/master/vignettes/api-packages.Rmd#appendix-api-key-best-practices)
it's unsafe to type the `TOKEN` just in the R script. It's better to use
environment variables set in `.Renviron` file.

So let's say you have named your bot `RTelegramBot` (it's the first question
you answered to the *BotFather* when creating it); you can open the `.Renviron` file with the R commands:

```{r, eval = FALSE}
file.edit(path.expand(file.path("~", ".Renviron")))
```

And put the following line with
your `TOKEN` in your `.Renviron`:

```{r, eval = FALSE}
R_TELEGRAM_BOT_RTelegramBot=TOKEN
```
If you follow the suggested `R_TELEGRAM_BOT_` prefix convention you'll be able
to use the `bot_token` function (otherwise you'll have to get
these variable from `Sys.getenv`).

After you've finished these steps **restart R** in order to have
working environment variables. You can then create the `Updater` object as:

```{r, eval = FALSE}
updater <- Updater(token = bot_token("RTelegramBot"))
```

### 2. The first function

Now, you can define a function that should process a specific type of update:

```{r, eval = FALSE}
start <- function(bot, update){
  bot$sendMessage(chat_id = update$message$chat_id,
                  text = sprintf("Hello %s!", update$message$from$first_name))
}
```

The goal is to have this function called every time the Bot receives a Telegram message that contains the `/start` command.
To accomplish that, you can use a `CommandHandler` (one of the provided `Handler` sub-classes) and register it in the `updaters`'s `dispatcher` (which is done with the `+` operator):

```{r, eval = FALSE}
start_handler <- CommandHandler("start", start)
updater <- updater + start_handler
```

### 3. Starting the Bot

And that's all you need. To start the bot, run:

```{r, eval = FALSE}
updater$start_polling()
```

Give it a try! Start a chat with your bot and issue the `/start` command - if all went right, it will reply.
