---
title: "The add operator"
author: "Ernest Benedito"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The add operator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The *add* operator (`+`, or more formally `+.TelegramObject`) is an S3 method for class `TelegramObject` that enables you to add any kind of `Handler` to an `Updater`'s `Dispatcher`.

### Example

Say you want to build a bot with a simple handler for the `/start` command:

```{r, eval = FALSE}
start <- function(bot, update){
  bot$sendMessage(chat_id = update$message$chat_id,
                  text = sprintf("Hello %s!",
                                 update$message$from$first_name))
}

start_handler <- CommandHandler("start", start)
```

You can then build your updater with:

```{r, eval = FALSE}
updater <- Updater("TOKEN") + start_handler
```

As things start to get more complex, you can chain multiple handlers in a single call:

```{r, eval = FALSE}
echo <- function(bot, update){
  bot$sendMessage(chat_id = update$message$chat_id,
                  text = update$message$text)
}

updater <- Updater("TOKEN") + CommandHandler("start", start) + MessageHandler(echo, MessageFilters$text)
```

And keep adding...

```{r, eval = FALSE}
caps <- function(bot, update, args){
  if (length(args > 0L)){
   	text_caps <- toupper(paste(args, collapse = " "))
   	bot$sendMessage(chat_id = update$message$chat_id,
   	                text = text_caps) 
  }
}

updater <- updater + CommandHandler("caps", caps, pass_args = TRUE)
```

Give it a try! Start polling the updater:

```{r, eval = FALSE}
updater$start_polling()
```

And send ***/start*** to the bot, ***/caps foo*** or just a simple text.

### How it works

The operator is indeed calling the `add_handler` method from an `Updater`'s `Dispatcher`. Then:

```{r, eval = FALSE}
updater <- updater + start_handler
```

Is equivalent to:

```{r, eval = FALSE}
updater$dispatcher$add_handler(start_handler)
```

Also, it works with `Dispatcher` objects:

```{r, eval = FALSE}
dispatcher <- updater$dispatcher
dispatcher <- dispatcher + start_handler
```

So, all in all, the `+.TelegramObject` operator simplifies the construction of an `Updater`. However, if you want to add a handler with advanced settings, let's say by controlling the `group` in which it is placed, you will need to make an `add_handler` call.
